---
title: "CodeBook"
author: "Shuguang Ji"
date: "December 26, 2015"
output: pdf_document
---
This is the code book for describing the variables.

One of the most exciting areas in all of data science right now is wearable computing - see for example this article . Companies like Fitbit, Nike, and Jawbone Up are racing to develop the most advanced algorithms to attract new users. The data linked to from the course website represent data collected from the accelerometers from the Samsung Galaxy S smartphone. A full description is available at the site where the data was obtained: 

http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones 

Here are the data for the project: 

https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip 

###1. Variable Descriptions


| Variable | Description
-----------|-------------
| activities | The activity performed
| subject | Subject ID
| tbodyacc-mean-x | Mean time for acceleration of body for X direction
| tbodyacc-mean-y | Mean time for acceleration of body for Y direction
| tbodyacc-mean-z | Mean time for acceleration of body for Z direction
| tbodyacc-std-x | Standard deviation of time for acceleration of body for X direction
| tbodyacc-std-y | Standard deviation of time for acceleration of body for Y direction
| tbodyacc-std-z | Standard deviation of time for acceleration of body for Z direction
| tgravityacc-mean-x | Mean time of acceleration of gravity for X direction
| tgravityacc-mean-y | Mean time of acceleration of gravity for Y direction
| tgravityacc-mean-z | Mean time of acceleration of gravity for Z direction
| tgravityacc-std-x | Standard deviation of time of acceleration of gravity for X direction
| tgravityacc-std-y | Standard deviation of time of acceleration of gravity for Y direction
| tgravityacc-std-z | Standard deviation of time of acceleration of gravity for Z direction
| tbodyaccjerk-mean-x | Mean time of body acceleration jerk for X direction
| tbodyaccjerk-mean-y | Mean time of body acceleration jerk for Y direction
| tbodyaccjerk-mean-z | Mean time of body acceleration jerk for Z direction
| tbodyaccjerk-std-x | Standard deviation of time of body acceleration jerk for X direction
| tbodyaccjerk-std-y | Standard deviation of time of body acceleration jerk for Y direction
| tbodyaccjerk-std-z | Standard deviation of time of body acceleration jerk for Z direction
| tbodygyro-mean-x | Mean body gyroscope measurement for X direction
| tbodygyro-mean-y | Mean body gyroscope measurement for Y direction
| tbodygyro-mean-z | Mean body gyroscope measurement for Z direction
| tbodygyro-std-x | Standard deviation of body gyroscope measurement for X direction
| tbodygyro-std-y | Standard deviation of body gyroscope measurement for Y direction
| tbodygyro-std-z | Standard deviation of body gyroscope measurement for Z direction
| tbodygyrojerk-mean-x | Mean jerk signal of body for X direction
| tbodygyrojerk-mean-y | Mean jerk signal of body for Y direction
| tbodygyrojerk-mean-z | Mean jerk signal of body for Z direction
| tbodygyrojerk-std-x | Standard deviation of jerk signal of body for X direction
| tbodygyrojerk-std-y | Standard deviation of jerk signal of body for Y direction
| tbodygyrojerk-std-z | Standard deviation of jerk signal of body for Z direction
| tbodyaccmag-mean | Mean magnitude of body Acc
| tbodyaccmag-std | Standard deviation of magnitude of body Acc
| tgravityaccmag-mean | Mean gravity acceleration magnitude
| tgravityaccmag-std | Standard deviation of gravity acceleration magnitude
| tbodyaccjerkmag-mean | Mean magnitude of body acceleration jerk
| tbodyaccjerkmag-std | Standard deviation of magnitude of body acceleration jerk
| tbodygyromag-mean | Mean magnitude of body gyroscope measurement
| tbodygyromag-std | Standard deviation of magnitude of body gyroscope measurement
| tbodygyrojerkmag-mean | Mean magnitude of body body gyroscope jerk measurement
| tbodygyrojerkmag-std | Standard deviation of magnitude of body body gyroscope jerk measurement
| fbodyacc-mean-x | Mean frequency of body acceleration for X direction
| fbodyacc-mean-y | Mean frequency of body acceleration for Y direction
| fbodyacc-mean-z | Mean frequency of body acceleration for Z direction
| fbodyacc-std-x | Standard deviation of frequency of body acceleration for X direction
| fbodyacc-std-y | Standard deviation of frequency of body acceleration for Y direction
| fbodyacc-std-z | Standard deviation of frequency of body acceleration for Z direction
| fbodyaccjerk-mean-x | Mean frequency of body accerlation jerk for X direction
| fbodyaccjerk-mean-y | Mean frequency of body accerlation jerk for Y direction
| fbodyaccjerk-mean-z | Mean frequency of body accerlation jerk for Z direction
| fbodyaccjerk-std-x | Standard deviation frequency of body accerlation jerk for X direction
| fbodyaccjerk-std-y | Standard deviation frequency of body accerlation jerk for Y direction
| fbodyaccjerk-std-z | Standard deviation frequency of body accerlation jerk for Z direction
| fbodygyro-mean-x | Mean frequency of body gyroscope measurement for X direction
| fbodygyro-mean-y | Mean frequency of body gyroscope measurement for Y direction
| fbodygyro-mean-z | Mean frequency of body gyroscope measurement for Z direction
| fbodygyro-std-x | Standard deviation frequency of body gyroscope measurement for X direction
| fbodygyro-std-y | Standard deviation frequency of body gyroscope measurement for Y direction
| fbodygyro-std-z | Standard deviation frequency of body gyroscope measurement for Z direction
| fbodyaccmag-mean | Mean frequency of body acceleration magnitude
| fbodyaccmag-std | Standard deviation of frequency of body acceleration magnitude
| fbodybodyaccjerkmag-mean | Mean frequency of body acceleration jerk magnitude
| fbodybodyaccjerkmag-std | Standard deviation of frequency of body acceleration jerk magnitude
| fbodybodygyromag-mean | Mean frequency of magnitude of body gyroscope measurement
| fbodybodygyromag-std | Standard deviation of frequency of magnitude of body gyroscope measurement
| fbodybodygyrojerkmag-mean | Mean frequency of magnitude of body gyroscope jerk measurement
| fbodybodygyrojerkmag-std | Standard deviation frequency of magnitude of body gyroscope jerk measurement
| | |

```{r include=FALSE}
#Please set your working directory properly. 
#0.Download the data set online.
fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
download.file(fileUrl, destfile = "data.zip")##No method="curl" used.
unzip("data.zip");
file.rename("UCI HAR Dataset","data");

#1.Merges the training and teh test sets to create one dataset.
TrainSet<-read.table("data/train/X_train.txt");
TestSet<-read.table("data/test/X_test.txt");
SetData<-rbind(TrainSet,TestSet);

TrainLabel<-read.table("data/train/y_train.txt");
TestLabel<-read.table("data/test/y_test.txt");
LabelData<-rbind(TrainLabel,TestLabel);

TrainSubj<-read.table("data/train/subject_train.txt");
TestSubj<-read.table("data/test/subject_test.txt");
SubjData<-rbind(TrainSubj,TestSubj);

names(SubjData)<-c("subject");
names(LabelData)<-c("activity");
DataFeatureNames<-read.table("data/features.txt",head=FALSE);
names(SetData)<-DataFeatureNames$V2;

DataCombine<-cbind(SubjData,LabelData);
Data<-cbind(SetData,DataCombine);

#2. Extracts only teh measurements on the mean and standard deviation for each measurement.
SubFeature<-DataFeatureNames$V2[grep("mean\\(\\)|std\\(\\)", DataFeatureNames$V2)];
SelectedNames<-c(as.character(SubFeature), "subject", "activity" );
Data_Mean_Sd<-subset(Data,select=SelectedNames);

#3. Uses descriptive activity names to name the activities in the data set.
DataDesc<-Data_Mean_Sd;
ActivityLabel<-read.table("data/activity_labels.txt",header = FALSE);
DataDesc$activity<-factor(DataDesc$activity);
DataDesc$activity<- factor(DataDesc$activity,labels=as.character(ActivityLabel$V2));

#4. Appropriately labels teh data set with descriptive varialbe names.
names(DataDesc)<-gsub("^t", "Time", names(DataDesc))
names(DataDesc)<-gsub("Acc", "Accelerometer", names(DataDesc))
names(DataDesc)<-gsub("Gyro", "Gyroscope", names(DataDesc))
names(DataDesc)<-gsub("Mag", "Magnitude", names(DataDesc))
names(DataDesc)<-gsub("^f", "Frequency", names(DataDesc))
names(DataDesc)<-gsub("BodyBody", "Body", names(DataDesc))

#5. From the data set in step 4, creates a second, independently tidy data
#set with the average of each variable for each activity and each subject. 
D2<-aggregate(x=DataDesc, by=list(activities=DataDesc$activity, subj=DataDesc$subject), FUN=mean)
D2<-D2[, !(colnames(D2) %in% c("subj", "activity"))]
str(D2)
write.table(D2,'submission.txt', row.names = F)
```

###2. Summary of merged data set in step 1

```{r}
str(Data)
```

###3. Summary of data set with mean and standard deviation values in step 2

```{r}
str(Data_Mean_Sd)
```

###4. Summary of data set with descriptinos from step 3 and 4

```{r}
str(DataDesc)
```

###5. Summary of data set generated in step 5

```{r}
str(D2)
```
